Predictions for detecting BHNS and other double compact objects binaries with LISA

### 2021-05-17 paper/tex/sections/comparisons.tex
rename figures

The discrepancy between their results and ours could be a result of different implicit assumptions in their population synthesis code, however we expect that BSE should be similar to COMPAS since it provided the basis of the COMPAS code. Another major difference is that, unlike this work, they assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular. We also improve upon this work by using a larger number of metallicity bins since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate \todo{needs citation}.

@@

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{compare_dco_1.png}

@@

    \includegraphics[width=\textwidth]{compare_dco_2.png}
    \caption{A table comparing previous studies of a similar nature to this work. The works listed in the table are \citet{Nelemans+2001,Belczynski+2010,Liu+2014,Lamberts+2018,Lau+2020,Breivik+2020,Sesana+2020}.}
    \label{fig:previous_studies}
\end{figure*}

>>>>

The discrepancy between their results and ours could be a result of different implicit assumptions in their population synthesis code, however we expect that BSE should be similar to COMPAS since it provided the basis of the COMPAS code. Another major difference is that, unlike this work, they assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular. We also improve upon this work by using a larger number of metallicity bins since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate \todo{needs citation, perhaps @Stephen knows?}.

@@

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{5_compare_dco_1.png}

@@

    \includegraphics[width=\textwidth]{5_compare_dco_2.png}
    \caption{A table comparing previous studies of a similar nature to this work. The works listed in the table are \citet{Nelemans+2001,Belczynski+2010,Liu+2014,Lamberts+2018,Lau+2020,Breivik+2020,Sesana+2020}.}
    \label{fig:previous_studies}
\end{figure*}
